Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-02-28 meta_analysis_sexual_selection_pop_fitness.Rmd
Luke initial work

---
title: "Effects of sexual selection on non-sexual fitness components: a meta-analysis"
subtitle: Supplementary Material
author: "Justin Cally, University of Melbourne"
output: html_notebook
---

```{r warning=FALSE, message=FALSE}
library(knitr)
library(pander)
library(compute.es)
library(metafor)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(MuMIn)
library(glmulti)
library(cowplot)
library(ggrepel)
library(reshape2)
```

# Methods

@@

##Literature Search (Extended methods from paper)

@@

1. We searched ISI Web of Science and Scopus on 9th June 2017. Notably, these resulted in a different set of returns (**PRISMA Figure**).

@@

@@

@@

In addition to studies found from the literature search we also included three relevant studies that were identified during scoping but not picked up in the subsequent formal searches (Partridge 1980; Price et al. 2010; Savic Veselinovic et al. 2013) that were missed by the database searches (**PRISMA Figure**).

4. After removing duplicates, we read the titles and abstracts of the remaining 1015 papers, and removed papers that were not relevant (typically because they were not an empirical study using experimental evolution). This left 130 papers, for which we read the full text and applied the following selection criteria:

@@

This latter criterion is likely to be contentious, because there is rarely enough data justify the assumption that a particular trait is (or is not) correlated with population fitness. We therefore relied on our best judgement when deciding which studies to exclude (see Table XXX). The inclusion/exlusion critera as applied to each study are detailed in an accompaning spreadsheet.

```{r}
Eligibility.criteria <- read.csv('Eligibility Workbook(22.02).csv', fileEncoding="UTF-8")
Eligibility.criteria %>% pander(split.cell = 20, split.table = 250, style = "grid")
```

##Data Extraction

The raw extracted data table is presented in the accompanying data folder. It details the type of data collected for each study (arithmatic means, SD, n, F-statistic, chi-squared, proportion etc.). The rules utilised were as follows:

@@

3. If means were not reported then we ecxtracted a summary statistic or proportion value, which we could later convert to Hedges g' using the _compute.es_ package. Summary statistics included _F_, _z_, _t_ and _chi^2^_. These conversions still required providing sample sizes for each treatment so these needed to be extractable from the study. Some summary statistics were obtained from generalized linear model summary tabels, others from straight forward ANOVAs and then some from more complex analysis such as proportional hazards statistical tests.

4. The covariates collected were extensive (**DATA TABLE**) and are discussed later. They were all regarded as potentially explaining trends in effect size or bias and hence were collected.

##Effect Size Calculation

> Not sure what to do about these calculations. I did not really lay them out neatly and the compute.es does not really return neat values. My calculations were done in a clunkier manual way. And are shown below.

**SS- will be group one with increased SS being group two**

####Almbro and Simmons 2014**

######Brood Number (No Distinction) 
```{r}
mes(15.4, 18, 10.071, 10.071, 207, 207, dig = 3)
```

######Strength (Stressed) 
```{r}
mes(0.047, 0.094, 0.05724, 0.16217, 91, 91, dig = 3)
```

##The Meta-Analysis Dataset

### Setup

Read in csv file 
```{r}
prelim.data <- read.csv('Preliminary data frame 22.2.18.csv')
kable(prelim.data)
```

###Explanation of Dataframe:

**Study ID**: An ID given to the published paper the effect size is sourced from

**Group ID**: An ID given to the research group that may have published several papers on the same species usuing the same or very similar experimental setup

**Species and Species ID**: Same thing

**SS Strength, Ratios and SS Density's (Column 7-9)**: Various ratios of the number of males to females and the total number of individuals kept together in an experiment

**Ratio Category**: A three level category for the ratio of males to females (high, medium, low).

**Density Category**: A three level category for the density of males to females (high, medium, low).

**SSS.Categorical**: A three level category for the **density & the ratio** of males to females (high medium, low).

**Post cop and Pre cop**: Whether a study allowed Pre/Post-copulatory sexual selection (1) or not (0)

**Blind**: Whether the study was blind or not

**Generations** The number of generations run before fitness outcomes were measured

**Enforced Monogamy**: Whether the study had the low sexual selection treatment as enforced monogamy (YES) or not (NO). Not all studies compared enforced monogamy and SS+ treatments. Some used FB vs MB, where FB is the SS (low intensity).

**Sex**: Whether the fitness outcome was measured for females (F), males (M) or both (B). Studies that reported 'both' would pool results from males and females.

**Ambiguous**: Is the fitness outcome ambiguous (YES) or not ambigous (NO). Ambiguous outcomes may be those that may not necessarily be directional, that is to say they may be a life history trait.

**Outcome Class**: Grouped as Direct, Indirect or Ambiguous.

**Environment**: In the methods of the papers included in this study it was usually stated whether additional modifications to the experimental lines were made. Briefly, this was usually a modification that made conditions more stressful such as using a novel food source or elevated mutation load, the effect sizes from these experimental lines are labelled as 'Stressed'. If it was clearly stated that there was no such modification it is labelled 'Unstressed'. However, sometimes the paper was ambiguous in what lines had added stress or the results from stressed and unstressed lines were pooled together, in this case we label it as 'Not Stated'.

**g**: Hedge's g calculated using the compute.es package

**var.g**: The within study variance associated with the effect size, g

**mean/sd/n.low/high**: The means, standard deviation and sample size for the low or high sexual selection treatments, used to calculate lnCVR (meta-analysis of variance). Rows without these values had hedges g' derived from summary statistics (F, z, chi-square etc.)

**JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.

_______________________________________________

### Factor and level data

A lot of the covariates are categorical, so here we assign them as factors and relevel them.

```{r}
prelim.data$Study.ID <- prelim.data$Study.ID %>% factor
prelim.data$Taxon <- prelim.data$Taxon %>% factor
prelim.data$Group.ID <- prelim.data$Group.ID %>% factor 
prelim.data$Authors <- prelim.data$Authors %>% factor
prelim.data$Environment <- prelim.data$Environment %>% factor %>% relevel(ref="Unstressed")
prelim.data$Sex <- prelim.data$Sex %>% factor %>% relevel(ref="B")
prelim.data$Ambiguous <- prelim.data$Ambiguous %>% factor
prelim.data$Species <- prelim.data$Species %>% factor
#Outcome.Class.2 is using the categories that were decided by survey. I am keeping both just to check them against each other (how much of a difference it makes)
prelim.data$Outcome.Class <- prelim.data$Outcome.Class %>% factor %>% relevel(ref="Indirect")
prelim.data$Enforced.Monogamy <- prelim.data$Enforced.Monogamy %>% factor %>% relevel(ref="NO")
prelim.data$Pre.cop <- prelim.data$Pre.cop %>% factor %>% relevel(ref="0")
prelim.data$Post.cop <- prelim.data$Post.cop %>% factor %>% relevel(ref="0")
prelim.data$Ratio.Category <- prelim.data$Ratio.Category %>% factor %>% relevel(ref="Low")
prelim.data$Density.Category <- prelim.data$Density.Category %>% factor %>% relevel(ref="Low")
prelim.data$SSS.Categorical <- prelim.data$SSS.Categorical %>% factor %>% relevel(ref="Low")
prelim.data$Blinding <- prelim.data$Blinding %>% factor
```

@@

###The Effect Size Dataset

@@

```{r}
n.blind.ones <- (sum(prelim.data$Blind == "Blind"))
n.stressed.ones <- 
prelim.data %>% summarise(Effect_sizes = n(), 
                       Publications = prelim.data$Study.ID %>% unique %>% length,
                       Blind_experiments = n.blind.ones,
                       Effect_sizes_.Stressedq = (sum(prelim.data$Environment == "Stressed")),
                       Effect_sizes_.Unstressedq = (sum(prelim.data$Environment == "Unstressed")),         
                       Effect_sizes_.Maleq = (sum(prelim.data$Sex == "M")),
                       Effect_sizes_.Femaleq = (sum(prelim.data$Sex == "F")),
                       Effect_sizes_.Both_sexesq = (sum(prelim.data$Sex == "B")),
                       Different_species =  prelim.data$Species %>% unique %>% length,
                       Effect_sizes_.Beetleq = sum(Taxon == "Beetle"),
                       Effect_sizes_.Flyq = sum(Taxon == "Fly"),
                       Effect_sizes_.Mouseq = sum(Taxon == "Mouse"),
                       Effect_sizes_.Nematodeq = sum(Taxon == "Nematode"),
                       Effect_sizes_.Miteq = sum(Taxon == "Mite"),
                       Effect_sizes_.Cricketq = sum(Taxon == "Cricket"),
                       Effect_sizes_.Guppyq = sum(Taxon == "Guppy")) %>% melt %>%
  mutate(variable = gsub("_", " ", variable),
         variable = gsub("[.]", "(", variable),
         variable = gsub("q", ")", variable)) %>% 
  rename_("n" = "value", " " = "variable") %>% pander(split.cell = 40, split.table = Inf)
```

###Forest plot using ggplot

@@

Using ggplot the forest plot is grouped according to environment and sex, with multiple effect sizes on one row for a given study

```{r, fig.height=30, fig.width=22.5}
#Create standard random effectrs model
forest.model <- rma(g, var.g, mods = ~ 1, method = "REML", data = prelim.data)

#Obtain residuals
resstandards <- (rstandard.rma.uni(forest.model, type="response"))

#Create new df with residuals replacing raw
df.forest.model <- prelim.data
df.forest.model$g <- resstandards$resid
df.forest.model$sei <- resstandards$se

#Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
df.forest.model$Outcome_f = factor(df.forest.model$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))

#define upper and lower bounds
df.forest.model$lowerci <- df.forest.model$g - 1.96*((df.forest.model$sei))
df.forest.model$upperci <- df.forest.model$g + 1.96*((df.forest.model$sei))

#Get author and year in one
df.forest.model$AuthorYear = paste(df.forest.model$Authors, df.forest.model$Year, sep=" ")

#Generate a plot
p.meta <- ggplot(df.forest.model, aes(y=reorder(AuthorYear, -g), x=g, xmin=lowerci, xmax=upperci, shape=Sex, color = Outcome.Class)) +
 #Add data points and color them black
geom_point(size=2)+
geom_errorbarh(data=df.forest.model, aes(xmin= lowerci, xmax = upperci) ,height=.1)+
  #Specify the limits of the x-axis and relabel it to something more meaningful
  scale_x_continuous(limits=c(-5,5), name='Standardized Mean Difference (g)')+
  #Give y-axis a meaningful label
  ylab('Reference')+
  #Add a vertical dashed line indicating an effect size of zero, for reference
  geom_vline(xintercept=0, color='black', linetype='dashed')+
  #Create sub-plots (i.e., facets) based on levels of setting
  #And allow them to have their own unique axes (so authors don't redundantly repeat)
  facet_grid(Outcome_f~., scales= 'free', space='free')+
  theme(strip.text.y = element_text(angle = 0))
p.meta
```

___________________
###Effect size of subgroups

>The following documents how i could run individual models for each outcome or outcome.class of interest and then plot them. This may be good to add to the above forest plot (in the form of a polygon; how many studies report their estimates) but at the same time, it just adds results from different subsetted models rather than one combined one (as we use when investigating sex and environment)

There is not really enough direct outcomes to analyse by itself so hence we combine with indirect later
```{r}
#Ambiguous outcomes

model.Ambiguous <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Ambiguous"), intercept = T ,data = prelim.data)

summary(model.Ambiguous)
```

```{r}
#Indirect outcomes

model.Indirect <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Indirect"), intercept = T ,data = prelim.data)

summary(model.Indirect)
```

```{r}
#Direct outcomes

model.Direct <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Direct"), data = prelim.data)

summary(model.Direct)
```

Now let's combine into a data frame and plot. The following plot could then be added to the large forest plot as summary polygons or summary points with error bars.

```{r}
#Data frame
Outcome.category <- c('Ambiguous', 'Indirect', 'Direct')
Estimate <- c(model.Ambiguous$b, model.Indirect$b, model.Direct$b)
l.ci <- c(model.Ambiguous$ci.lb, model.Indirect$ci.lb, model.Direct$ci.lb)
u.ci <- c(model.Ambiguous$ci.ub, model.Indirect$ci.ub, model.Direct$ci.ub)
data.1 <- data.frame(Outcome.category, Estimate, l.ci, u.ci)

#plot

data.1 %>% ggplot(aes(x = Estimate, y= Outcome.category)) + 
  geom_point() +
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = l.ci, xmax = u.ci), height = 0, size=1) +
  ylab("Outcome Category")+
  xlab("Effect Size")+
  xlim(-.2, .5)+
  ggtitle('Meta-Analysis Results')
```

@@

###Model predictions

####Does the effect of sexual selection differ between species?

@@

#RWe need to make sure the factors are leveled in the same order as we write our prediction function (below)
restricted.data$Environment <- restricted.data$Environment %>% factor %>% relevel(ref="Unstressed")
restricted.data$Sex <- restricted.data$Sex %>% factor %>% relevel(ref="M")
restricted.data$Outcome.Class <- restricted.data$Outcome.Class %>% factor %>% relevel(ref="Indirect")

#run model again with restricted data 
model.complete <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex + Environment + Taxon + Sex:Environment, 
                         random = ~ 1 | Study.ID/Outcome, 
                         method = "REML", 
                         data = restricted.data)

#Note that the data is subsetted
summary(model.complete)

@@

Note that to get vertical position dodge to use in the ggplot meta-analysis we need to utilise a vertical position dodge. We can obtain this formula from the following github page by Jared Lander: https://github.com/jaredlander/coefplot/blob/master/R/position.r
```{r include=FALSE}
# Detect and prevent collisions.
# Powers dodging, stacking and filling.
collidev <- function(data, height = NULL, name, strategy, check.height = TRUE) {
    # Determine height
    if (!is.null(height)) {
        # height set manually
        if (!(all(c("ymin", "ymax") %in% names(data)))) {
            data$ymin <- data$y - height / 2
            data$ymax <- data$y + height / 2
        }
    } else {
        if (!(all(c("ymin", "ymax") %in% names(data)))) {
            data$ymin <- data$y
            data$ymax <- data$y
        }

        # height determined from data, must be floating point constant
        heights <- unique(data$ymax - data$ymin)
        heights <- heights[!is.na(heights)]

        #   # Suppress warning message since it's not reliable
        #     if (!zero_range(range(heights))) {
        #       warning(name, " requires constant height: output may be incorrect",
        #         call. = FALSE)
        #     }
        height <- heights[1]
    }

    # Reorder by x position, relying on stable sort to preserve existing
    # ordering, which may be by group or order.
    data <- data[order(data$ymin), ]

    # Check for overlap
    intervals <- as.numeric(t(unique(data[c("ymin", "ymax")])))
    intervals <- intervals[!is.na(intervals)]

    if (length(unique(intervals)) > 1 & any(diff(scale(intervals)) < -1e-6)) {
        warning(name, " requires non-overlapping y intervals", call. = FALSE)
        # This is where the algorithm from [L. Wilkinson. Dot plots.
        # The American Statistician, 1999.] should be used
    }

    if (!is.null(data$xmax)) {
        plyr::ddply(data, "ymin", strategy, height = height)
    } else if (!is.null(data$x)) {
        data$xmax <- data$x
        data <- plyr::ddply(data, "ymin", strategy, height = height)
        data$x <- data$xmax
        data
    } else {
        stop("Neither x nor xmax defined")
    }
}

# Stack overlapping intervals.
# Assumes that each set has the same horizontal position
pos_stackv <- function(df, height) {
    if (nrow(df) == 1) return(df)

    n <- nrow(df) + 1
    x <- ifelse(is.na(df$x), 0, df$x)
    if (all(is.na(df$y))) {
        heights <- rep(NA, n)
    } else {
        heights <- c(0, cumsum(x))
    }

    df$xmin <- heights[-n]
    df$xmax <- heights[-1]
    df$x <- df$xmax
    df
}

# Stack overlapping intervals and set height to 1.
# Assumes that each set has the same horizontal position.
pos_fillv <- function(df, height) {
    stacked <- pos_stackv(df, height)
    stacked$xmin <- stacked$xmin / max(stacked$xmax)
    stacked$xmax <- stacked$xmax / max(stacked$xmax)
    stacked$x <- stacked$xmax
    stacked
}

# Dodge overlapping interval.
# Assumes that each set has the same horizontal position.
pos_dodgev <- function(df, height) {
    n <- length(unique(df$group))
    if (n == 1) return(df)

    if (!all(c("ymin", "ymax") %in% names(df))) {
        df$ymin <- df$y
        df$ymax <- df$y
    }

    d_height <- max(df$ymax - df$ymin)

    # df <- data.frame(n = c(2:5, 10, 26), div = c(4, 3, 2.666666,  2.5, 2.2, 2.1))
    # ggplot(df, aes(n, div)) + geom_point()

    # Have a new group index from 1 to number of groups.
    # This might be needed if the group numbers in this set don't include all of 1:n
    groupidy <- match(df$group, sort(unique(df$group)))

>>>>

---
title: 'Effects of sexual selection on non-sexual fitness components: a meta-analysis'
author: "Justin Cally, University of Melbourne"
subtitle: Supplementary Material
output:
  html_document:
    toc: true # table of content true
    toc_float: true # make 
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  ## if you want number sections at each table header
    theme: yeti # lovely fonts and colours
    code_folding: hide # awesome buttons to show/hide the code
  pdf_document: default
---

```{r warning=FALSE, message=FALSE, results='hide'}
library(knitr)
library(pander)
library(compute.es)
library(metafor)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(MuMIn)
library(glmulti)
library(cowplot)
library(ggrepel)
library(reshape2)
source("Vdodge_function.R") # nice function for ggplot
```

```{r echo=FALSE, results='hide'}
library(knitr) # set up cacheing to save time when re-building the html document
```
`r opts_chunk$set(cache=TRUE)`

## Supplementary Methods

@@

### Literature Search

@@

1. We searched ISI Web of Science and Scopus on 9th June 2017. The two search engines produded a somewhat different set of papers (**PRISMA Figure**).

@@

We used the following search on ISI Web of Science:

@@

We used the following search on Scopus:

@@

### Additions to the literature search

In addition to studies found from the literature search we also included three relevant studies that we found, which were not picked up in the subsequent formal searches (Partridge 1980; Price et al. 2010; Savic Veselinovic et al. 2013; **PRISMA Figure**).

### Data extraction

After removing duplicates papers recovered from both ISI and Scopus, we read the titles and abstracts of the remaining 1015 papers, and removed papers that were not relevant (typically because they were not an empirical study using experimental evolution). This left 130 papers, for which we read the full text and applied the following selection criteria:

@@

This latter criterion is likely to be contentious, because there is rarely enough data justify the assumption that a particular trait is (or is not) correlated with population fitness. We therefore relied on our best judgement when deciding which studies to exclude (see Table XXX). The inclusion/exlusion critera as applied to each study are detailed in **Table S1**.

**Table S1:** WRITE TABLE LEGEND.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
Eligibility.criteria <- read.csv('data/Eligibility Workbook(22.02).csv', 
                                 fileEncoding="UTF-8")
Eligibility.criteria %>% 
  pander(split.cell = 40, split.table = Inf)
```

### Effect Size Calculation

A spreadsheet describing the data that was extracted from each of the included studies is included as supplementary material. It details the type of data collected for each study (arithmatic means, SD, n, F-statistic, chi-squared, proportion etc.). The rules utilised were as follows:

@@

3. If means were not reported then we extracted a summary statistic or proportion value, which we could later convert to Hedges g' using the _compute.es_ package. Summary statistics included _F_, _z_, _t_ and _chi^2^_. These conversions still required providing sample sizes for each treatment so these needed to be extractable from the study. Some summary statistics were obtained from generalized linear model summary tabels, others from straight forward ANOVAs and then some from more complex analysis such as proportional hazards statistical tests.

4. We also collected various covariates for some of the studies (**DATA TABLE**), which are discussed later.

## The effect size dataset

### Table of effect sizes

**Table S2:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
# Load the data and clean up the variable formats
prelim.data <- read.csv('data/Preliminary data frame 22.2.18.csv')
prelim.data$Study.ID <- prelim.data$Study.ID %>% factor()
prelim.data$Taxon <- prelim.data$Taxon %>% factor()
prelim.data$Group.ID <- prelim.data$Group.ID %>% factor()
prelim.data$Authors <- prelim.data$Authors %>% factor()
prelim.data$Environment <- prelim.data$Environment %>% factor %>% relevel(ref="Unstressed")
prelim.data$Sex <- prelim.data$Sex %>% factor %>% relevel(ref="B")
prelim.data$Ambiguous <- prelim.data$Ambiguous %>% factor()
prelim.data$Species <- prelim.data$Species %>% factor()
#Outcome.Class.2 is using the categories that were decided by survey. I am keeping both just to check them against each other (how much of a difference it makes)
prelim.data$Outcome.Class <- prelim.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
prelim.data$Enforced.Monogamy <- prelim.data$Enforced.Monogamy %>% factor() %>% relevel(ref="NO")
prelim.data$Pre.cop <- prelim.data$Pre.cop %>% factor() %>% relevel(ref="0")
prelim.data$Post.cop <- prelim.data$Post.cop %>% factor() %>% relevel(ref="0")
prelim.data$Ratio.Category <- prelim.data$Ratio.Category %>% factor() %>% relevel(ref="Low")
prelim.data$Density.Category <- prelim.data$Density.Category %>% factor() %>% relevel(ref="Low")
prelim.data$SSS.Categorical <- prelim.data$SSS.Categorical %>% factor() %>% relevel(ref="Low")
prelim.data$Blinding <- prelim.data$Blinding %>% factor()

prelim.data %>% pander(split.cell = 40, split.table = Inf)
```

**Study ID**: An ID given to the published paper the effect size is sourced from
**Group ID**: An ID given to the research group that may have published several papers on the same species usuing the same or very similar experimental setup
**Species and Species ID**: Same thing
**SS Strength, Ratios and SS Density's (Column 7-9)**: Various ratios of the number of males to females and the total number of individuals kept together in an experiment
**Ratio Category**: A three level category for the ratio of males to females (high, medium, low).
**Density Category**: A three level category for the density of males to females (high, medium, low).
**SSS.Categorical**: A three level category for the **density & the ratio** of males to females (high medium, low). 
**Post cop and Pre cop**: Whether a study allowed Pre/Post-copulatory sexual selection (1) or not (0)
**Blind**: Whether the study was blind or not
**Generations** The number of generations run before fitness outcomes were measured
**Enforced Monogamy**: Whether the study had the low sexual selection treatment as enforced monogamy (YES) or not (NO). Not all studies compared enforced monogamy and SS+ treatments. Some used FB vs MB, where FB is the SS (low intensity). 
**Sex**: Whether the fitness outcome was measured for females (F), males (M) or both (B). Studies that reported 'both' would pool results from males and females.
**Ambiguous**: Is the fitness outcome ambiguous (YES) or not ambigous (NO). Ambiguous outcomes may be those that may not necessarily be directional, that is to say they may be a life history trait. 
**Outcome Class**: Grouped as Direct, Indirect or Ambiguous.
**Environment**: In the methods of the papers included in this study it was usually stated whether additional modifications to the experimental lines were made. Briefly, this was usually a modification that made conditions more stressful such as using a novel food source or elevated mutation load, the effect sizes from these experimental lines are labelled as 'Stressed'. If it was clearly stated that there was no such modification it is labelled 'Unstressed'. However, sometimes the paper was ambiguous in what lines had added stress or the results from stressed and unstressed lines were pooled together, in this case we label it as 'Not Stated'. 
**g**: Hedge's g calculated using the compute.es package
**var.g**: The within study variance associated with the effect size, g
**mean/sd/n.low/high**: The means, standard deviation and sample size for the low or high sexual selection treatments, used to calculate lnCVR (meta-analysis of variance). Rows without these values had hedges g' derived from summary statistics (F, z, chi-square etc.)
**JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.

@@

### Table of sample sizes

@@

**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r message=FALSE}
n.blind.ones <- (sum(prelim.data$Blind == "Blind"))
prelim.data %>% 
  summarise(
    Effect_sizes_.Totalq = n(), 
    Publications = prelim.data$Study.ID %>% unique() %>% length(),
    Blind_experiments = n.blind.ones,
    Effect_sizes_.Stressedq = (sum(prelim.data$Environment == "Stressed")),
    Effect_sizes_.Unstressedq = (sum(prelim.data$Environment == "Unstressed")),         
    Effect_sizes_.Maleq = (sum(prelim.data$Sex == "M")),
    Effect_sizes_.Femaleq = (sum(prelim.data$Sex == "F")),
    Effect_sizes_.Both_sexesq = (sum(prelim.data$Sex == "B")),
    Different_species =  prelim.data$Species %>% unique() %>% length(),
    Effect_sizes_.Beetleq = sum(Taxon == "Beetle"),
    Effect_sizes_.Flyq = sum(Taxon == "Fly"),
    Effect_sizes_.Mouseq = sum(Taxon == "Mouse"),
    Effect_sizes_.Nematodeq = sum(Taxon == "Nematode"),
    Effect_sizes_.Miteq = sum(Taxon == "Mite"),
    Effect_sizes_.Cricketq = sum(Taxon == "Cricket"),
    Effect_sizes_.Guppyq = sum(Taxon == "Guppy")) %>% melt() %>%
  mutate(variable = gsub("_", " ", variable),
         variable = gsub("[.]", "(", variable),
         variable = gsub("q", ")", variable)) %>% 
  rename_("n" = "value", " " = "variable") %>% 
  pander(split.cell = 40, split.table = Inf)
```

### Forest plot

@@

> Luke says: if you are plotting RESIDUAL effect sizes, doesn't that mean this plots shows each effect size, relative to the grand mean effect size? Like, -0.05 means it is below average, but the effect is still positive since the grand mean is +0.1. This is probably not what we want.

> I have modified the code below so that it plots the resid + the grand mean. But I think since model is intercept only, this might be the same thing as the raw data... not sure. Have a think, or just plot all the raw effect sizes +/- their 95% CIs, instead of the residuals.

> Also try to make it clear what positive g means (I guess positive g means higher fitness when SS is present/strong?)

```{r, fig.height=25, fig.width=10}
# Run standard random effects model
forest.model <- rma(g, var.g, mods = ~ 1, method = "REML", data = prelim.data)

# Obtain residuals
resstandards <- (rstandard.rma.uni(forest.model, type="response"))

# Obtain grand mean effect size    <- ADDED BY LUKE
grand.mean <- as.numeric(forest.model$b)

# Create new df with residuals replacing raw
df.forest.model <- prelim.data                     # <- Luke says: you could just use prelim.data itself, not the residuals?
df.forest.model$g <- resstandards$resid + grand.mean   # <- ADDED BY LUKE
df.forest.model$sei <- resstandards$se

# Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
df.forest.model$Outcome_f = factor(df.forest.model$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))

# define upper and lower bounds
df.forest.model$lowerci <- df.forest.model$g - 1.96*((df.forest.model$sei))
df.forest.model$upperci <- df.forest.model$g + 1.96*((df.forest.model$sei))

# Get author and year in one
short.author.names <- data.frame(long = df.forest.model$Authors %>% unique(),
                                 short = df.forest.model$Authors %>% unique() %>% 
  as.character() %>% 
  strsplit(split = ",") %>% 
  sapply(FUN=function(x) x[1])) %>%
  left_join(df.forest.model %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
  mutate(suffix = "")

# Sometimes there are multiple papers with the same first author from teh same year. Name these 2010a, 2010b etc
dups <- with(short.author.names, table(short, Year)) %>% melt()
dups <- dups[dups$value > 1, ]
for(i in 1:nrow(dups)){
  short.author.names$suffix[
    short.author.names$short == dups$short[i] &
      short.author.names$Year == dups$Year[i]] <- letters[1:dups$value[i]]
}

# Add the AuthorYear column to the dataframe of effect sizes
short.author.names <- short.author.names %>%
  mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
  select(long, AuthorYear)
df.forest.model <- df.forest.model %>% 
  left_join(short.author.names, by = c("Authors" = "long"))

#Generate a plot
p.meta <- df.forest.model %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(y=reorder(AuthorYear, -g), x = g, shape = Sex, color = Outcome.Class)) +
  geom_errorbarh(aes(xmin = lowerci, xmax = upperci), height = 0.1) +
  geom_point(size = 2) +  #Add data points and color them black
  scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g)') +
  scale_color_discrete(name = "Relationship\nto fitness") + 
  ylab('Reference') + 
  geom_vline(xintercept=0, color='black', linetype='dashed')+
  facet_grid(Outcome_f~., scales= 'free', space='free')+
  theme(strip.text.y = element_text(angle = 0))
ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 25, width = 12)
p.meta
```
<br></br>
**Figure 1:** Forest plot of effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes.

___________________

### Effect size differs depending on the response variable

>The following documents how I could run individual models for each outcome or outcome.class of interest and then plot them. This may be good to add to the above forest plot (in the form of a polygon; how many studies report their estimates) but at the same time, it just adds results from different subsetted models rather than one combined one (as we use when investigating sex and environment)

> Nice idea, but I think the correct way to do this is to fit Outcome.class as a moderator, and then use predict() to find the average effect size within each of the 3 levels, as you have done below. I coded something below, but it's wrong:

```{r}
model.outcome.class <- rma(g, var.g,
                           mods = ~ Outcome.Class, 
                           method = "REML", 
                           intercept = TRUE, 
                           data = prelim.data)

# Get the intercept (i.e. the grand mean for 'ambiguous', and the effects for the others)
mod.table <- do.call("cbind", model.outcome.class[names(model.outcome.class) %in% c("b", "ci.lb", "ci.ub")])

data.frame(Outcome.class = c("Ambiguous", "Direct", "Indirect"),
           mod.table) %>%
  ggplot(aes(y = Outcome.class, x = V1))  +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height=0) +
  geom_point() + 
  xlab("Effect size and 95% CIs")
```

<!-- There is not really enough direct outcomes to analyse by itself so hence we combine with indirect later -->
<!-- ```{r} -->
<!-- #Ambiguous outcomes -->

<!-- model.Ambiguous <- rma(g, var.g, -->
<!--                        mods = ~ 1,  -->
<!--                        method = "REML",  -->
<!--                        subset = (Outcome.Class == "Ambiguous"),  -->
<!--                        intercept = TRUE,  -->
<!--                        data = prelim.data) -->

<!-- summary(model.Ambiguous) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #Indirect outcomes -->

<!-- model.Indirect <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Indirect"), intercept = T ,data = prelim.data) -->

<!-- summary(model.Indirect) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #Direct outcomes -->

<!-- model.Direct <- rma(g, var.g, mods = ~ 1, method = "REML", subset = (Outcome.Class == "Direct"), data = prelim.data) -->

<!-- summary(model.Direct) -->
<!-- ``` -->

<!-- Now let's combine into a data frame and plot. The following plot could then be added to the large forest plot as summary polygons or summary points with error bars.  -->

<!-- ```{r} -->
<!-- #Data frame -->
<!-- Outcome.category <- c('Ambiguous', 'Indirect', 'Direct') -->
<!-- Estimate <- c(model.Ambiguous$b, model.Indirect$b, model.Direct$b) -->
<!-- l.ci <- c(model.Ambiguous$ci.lb, model.Indirect$ci.lb, model.Direct$ci.lb) -->
<!-- u.ci <- c(model.Ambiguous$ci.ub, model.Indirect$ci.ub, model.Direct$ci.ub) -->
<!-- data.1 <- data.frame(Outcome.category, Estimate, l.ci, u.ci) -->

<!-- #plot -->

<!-- data.1 %>% ggplot(aes(x = Estimate, y= Outcome.category)) +  -->
<!--   geom_point() + -->
<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") +  -->
<!--   geom_errorbarh(aes(xmin = l.ci, xmax = u.ci), height = 0, size=1) + -->
<!--   ylab("Outcome Category")+ -->
<!--   xlab("Effect Size")+ -->
<!--   xlim(-.2, .5)+ -->
<!--   ggtitle('Meta-Analysis Results') -->
<!-- ``` -->

@@

### Effect size differs between taxa

@@

# Make sure the factors are leveled in the same order as we write our prediction function (below)
restricted.data$Environment <- restricted.data$Environment %>% factor %>% relevel(ref="Unstressed")
restricted.data$Sex <- restricted.data$Sex %>% factor %>% relevel(ref="M")
restricted.data$Outcome.Class <- restricted.data$Outcome.Class %>% factor %>% relevel(ref="Indirect")

# run meta-analysis using the restricted data, and moderators
model.complete <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex + Environment + Taxon + Sex:Environment, 
                         random = ~ 1 | Study.ID/Outcome, 
                         method = "REML", 
                         data = restricted.data)

summary(model.complete) 
```

@@
